A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2024-11-29 manuscript/manuscript.qmd
installed webshot2
removed landscape condition

library(here)
library(dplyr)
library(knitr)
library(captioner)
library(gt)
library(readxl)
library(fs)

@@

::: landscape
# Tables {.unnumbered}

@@

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/figures/process.png)
:::

>>>>

library(here)
library(dplyr)
library(knitr)
library(captioner)
library(gt)
library(readxl)
library(fs)
library(webshot2)

@@

# Tables {.unnumbered}

@@

[View figure in higher resolution here](https://github.com/janickweberpals/encore-process-manuscript/blob/main/figures/process.png)
